A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-17 introduction.tex
Adding comments about EM followup
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@633 ccdd05d5-56c1-461a-bf98-85f6876523b4

Beyond raw throughput, the ability to detect signals in near realtime will
become increasingly valuable as the gravitational-wave detection horizon pushes
outward. Having an electromagnetic or neutrino counterpart to a
gravitational-wave detection would not only increase the confidence in the
detection but will also greatly increase the astrophysical information
available from the event. Most models that predict simultaneous
gravitational-wave and electromagnetic observations also predict that the peak
amplitude of electromagetic radiation will occur soon after gravitational-wave
emission~\cite{sylvestre2003}. Thus in order to maximize the chance of a
successful electromagnetic followup the latency of gravitational-wave signal
analysis must be made minimal.

>>>>

Beyond raw throughput, the ability to detect signals in near realtime will
become increasingly valuable as the gravitational-wave detection horizon pushes
outward. Having an electromagnetic or neutrino counterpart to a
gravitational-wave detection would not only increase the confidence in the
detection but will also greatly increase the astrophysical information
available from the event. \editorial{dk: I don't think this is true for
neutrino counterparts. Just as there is no need to point GW detectors, there is
no need to point neutrino detectors so the association can easily be done
offline.} Most models that predict simultaneous gravitational-wave and
electromagnetic observations also predict that the peak amplitude of
electromagetic radiation will occur soon after gravitational-wave
emission~\cite{sylvestre2003}. \editorial{dk: This is not true for all EM
bands.  Radio afterglows from short GRBs are not expected to be seen until 1
month after observation and then observable for several months.} Thus in order
to maximize the chance of a successful electromagnetic followup the latency of
gravitational-wave signal analysis must be made minimal.
